Simple and Compositional Reification of Monadic Embedded Languages

### 2013-11-04 src2/bb/body.tex
update

\pagebreak
\begin{small} 
\begin{verbatim}
type Name = String

@@

@@

%\pagebreak
\begin{small} 
\begin{verbatim}
runCompile :: Program a -> Prg
runCompile prg = snd $ compile s prg 
  where 
    s = newNameSupply

compile :: NameSupply -> Program a -> (a, Prg) 
compile s Move = ((),PMove)
compile s TurnRight = ((),PTurnRight)
compile s TurnLeft  = ((),PTurnLeft)
compile s Sensor    = (Var nom,PSensor nom)
  where
    v   = supplyValue s
    nom = "v" ++ show v 
compile s (Cond b p1 p2) = 
    ((),bp `PSeq` PCond b' p1' p2') 
  where
    (s1,s2,s3) = split3 s
    (b',bp)    = compile s1 b
    (a1,p1')   = compile s2 p1
    (a2,p2')   = compile s3 p2
compile s (While wp prg) = ((),PWhile nom nwp prg') 
  where
    (s1,s2,s3) = split3 s
    (b,wp')    = compile s1 wp
    (c,prg')   = compile s2 prg 
    nom        = "v" ++ (show $ supplyValue s3)
    nwp        = (wp' `PSeq` PAssign nom b) 
compile s (Return a) = (a,PSkip)
compile s (Bind pa f) = (b, prg1 `PSeq` prg2) 
  where
    (s1,s2)  = split2 s
    (a,prg1) = compile s1 pa
    (b,prg2) = compile s2 (f a) 
\end{verbatim}
\end{small}

@@

instance Compile (SensorOp x) where
  compile s Sensor = (Var nom, PSensor nom)
    where v   = supplyValue s
          nom = "v" ++ show v
\end{verbatim}
\pagebreak
\begin{verbatim}
instance Compile x => Compile (CondOp x) where
  compile s (Cond b p1 p2) = 
    ((),bp `PSeq` PCond b' p1' p2') 
    where (s1,s2,s3) = split3 s
          (b',bp)    = compile s1 b
          (a1,p1')   = compile s2 p1
          (a2,p2')   = compile s3 p2 
\end{verbatim}
\end{small}
%% instance Compile x => Compile (CondOp x) where
%%   compile s (Cond b p1 p2) = ((),PCond b p1' p2') 
%%     where
%%       (s1,s2) = split2 s
%%       (a1,p1') = compile s1 p1
%%       (a2,p2') = compile s2 p2 
%\pagebreak
\begin{small}
\begin{verbatim}
instance Compile x => Compile (WhileOp x) where
  compile s (While wp p) = ((),PWhile nom nwp p')
    where (s1,s2,s3) = split3 s
          (b,wp')    = compile s1 wp
          (c,p')     = compile s2 p
          nom        = "v" ++ (show $ supplyValue s3)
          nwp        = wp' `PSeq` PAssign nom b

>>>>

% \pagebreak
\begin{small} 
\begin{verbatim}
type Name = String

@@

\pagebreak

@@

%\pagebreak
\begin{small} 
\begin{verbatim}
runCompile :: Program a -> Prg
runCompile prg = snd $ compile s prg 
  where 
    s = newNameSupply
\end{verbatim}
\end{small}

\begin{small}
\begin{verbatim}
compile :: NameSupply -> Program a -> (a, Prg) 
compile s Move = ((),PMove)
compile s TurnRight = ((),PTurnRight)
compile s TurnLeft  = ((),PTurnLeft)
\end{verbatim}
\end{small}

\pagebreak

\begin{small}
\begin{verbatim}
compile s Sensor    = (Var nom,PSensor nom)
  where
    v   = supplyValue s
    nom = "v" ++ show v 
compile s (Cond b p1 p2) = 
    ((),bp `PSeq` PCond b' p1' p2') 
  where
    (s1,s2,s3) = split3 s
    (b',bp)    = compile s1 b
    (a1,p1')   = compile s2 p1
    (a2,p2')   = compile s3 p2
compile s (While wp prg) = ((),PWhile nom nwp prg') 
  where
    (s1,s2,s3) = split3 s
    (b,wp')    = compile s1 wp
    (c,prg')   = compile s2 prg 
    nom        = "v" ++ (show $ supplyValue s3)
    nwp        = (wp' `PSeq` PAssign nom b) 
compile s (Return a) = (a,PSkip)
compile s (Bind pa f) = (b, prg1 `PSeq` prg2) 
  where
    (s1,s2)  = split2 s
    (a,prg1) = compile s1 pa
    (b,prg2) = compile s2 (f a) 
\end{verbatim}
\end{small}

@@

instance Compile (SensorOp x) where
  compile s Sensor = (Var nom, PSensor nom)
    where v   = supplyValue s
          nom = "v" ++ show v
\end{verbatim}
% \pagebreak
\begin{verbatim}
instance Compile x => Compile (CondOp x) where
  compile s (Cond b p1 p2) = 
    ((),bp `PSeq` PCond b' p1' p2') 
    where (s1,s2,s3) = split3 s
          (b',bp)    = compile s1 b
          (a1,p1')   = compile s2 p1
          (a2,p2')   = compile s3 p2 
\end{verbatim}
\end{small}
%% instance Compile x => Compile (CondOp x) where
%%   compile s (Cond b p1 p2) = ((),PCond b p1' p2') 
%%     where
%%       (s1,s2) = split2 s
%%       (a1,p1') = compile s1 p1
%%       (a2,p2') = compile s2 p2 
%\pagebreak
\begin{small}
\begin{verbatim}
instance Compile x => Compile (WhileOp x) where
  compile s (While wp p) = ((),PWhile nom nwp p')
    where (s1,s2,s3) = split3 s
          (b,wp')    = compile s1 wp
          (c,p')     = compile s2 p
          nom        = "v" ++ (show $ supplyValue s3)
          nwp        = wp' `PSeq` PAssign nom b
